\chapter{Ephesians 6}









\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{MARCHING ORDERS}}\\ (Ephesians 6:1-24) \begin{compactenum}[I.][8]
    \item \textbf{Response to Authority} \index[scripture]{Ephesians!Ephesians 6:01}\index[scripture]{Ephesians!Ephesians 6:05} (Ephesians 6:1, 5)
    \item \textbf{Responsibility of Admonition} \index[scripture]{Ephesians!Ephesians 6:04} (Ephesians 6:4)
    \item Be \textbf{Ready to put on Armour} \index[scripture]{Ephesians!Ephesians 6:11}\index[scripture]{Ephesians!Ephesians 6:13} (Ephesians 6:11, 13)
    \item \textbf{Recognize the Adversary} \index[scripture]{Ephesians!Ephesians 6:12} (Ephesians 6:12)
    \item \textbf{Requests \& Appeals} \index[scripture]{Ephesians!Ephesians 6:18} (Ephesians 6:18)
    \item \textbf{Role as Ambassadors} \index[scripture]{Ephesians!Ephesians 6:20} (Ephesians 6:20)
\end{compactenum}}

% \textcolor[cmyk]{0.99998,1,0,0}{
% \footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/N/Eph/1}{\textcolor[cmyk]{0.99998,1,0,0}{Ephesians Audio}}}
\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/N/Eph/1}{\textcolor[cmyk]{0.99998,1,0,0}{Ephesians Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Children, \fcolorbox{bone}{lime}{obey} your parents in the Lord: for this is right.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{Honour thy father and mother; (which is the first commandment with promise;)}
[3] \textcolor[cmyk]{0.99998,1,0,0}{That it may be well with thee, and thou mayest live long on the earth.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And, ye fathers, provoke not your children \fcolorbox{bone}{bone}{to} wrath: but bring them up in the nurture and \fcolorbox{bone}{lime}{admonition} of the Lord.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{Servants, be \fcolorbox{bone}{lime}{obedient} \fcolorbox{bone}{bone}{to} them that are \emph{your} masters according \fcolorbox{bone}{bone}{to} the flesh, with fear and trembling, in singleness of your heart, as unto Christ;}
[6] \textcolor[cmyk]{0.99998,1,0,0}{Not with eyeservice, as menpleasers; but as the servants of Christ, doing the will of God from the heart;}
[7] \textcolor[cmyk]{0.99998,1,0,0}{With good will doing service, as \fcolorbox{bone}{bone}{to} the Lord, and not \fcolorbox{bone}{bone}{to} men:}
[8] \textcolor[cmyk]{0.99998,1,0,0}{Knowing that whatsoever good thing any man doeth, the same shall he receive of the Lord, whether \emph{he} \emph{be} bond or free.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{And, ye masters, do the same things unto them, forbearing threatening: knowing that your Master also is in heaven; neither is there respect of persons with him.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{Finally, my brethren, be strong in the Lord, and in the power of his might.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{Put on the whole \fcolorbox{bone}{lime}{armour} of God, that ye may be able \fcolorbox{bone}{bone}{to} stand against the wiles of the devil.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{For we wrestle not against flesh and blood, but against principalities, against powers, against the rulers of the darkness of this world, against \fcolorbox{bone}{lime}{spiritual wickedness} in high \emph{places}.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore take unto you the whole \fcolorbox{bone}{lime}{armour} of God, that ye may be able \fcolorbox{bone}{bone}{to} withstand in the evil day, and having done all, \fcolorbox{bone}{bone}{to} stand.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{Stand therefore, having your loins girt about with truth, and having on the breastplate of \fcolorbox{bone}{MYGOLD}{righteousness};}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And your feet shod with the preparation of the gospel of peace;}
[16] \textcolor[cmyk]{0.99998,1,0,0}{Above all, taking the shield of faith, wherewith ye shall be able \fcolorbox{bone}{bone}{to} quench all the fiery darts of the wicked.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And take the helmet of salvation, and the sword of the Spirit, which is the word of God:}
[18] \textcolor[cmyk]{0.99998,1,0,0}{Praying always with all prayer and \fcolorbox{bone}{lime}{supplication} in the Spirit, and watching thereunto with all perseverance and supplication for all saints;}
[19] \textcolor[cmyk]{0.99998,1,0,0}{And for me, that utterance may be given unto me, that I may open my mouth boldly, \fcolorbox{bone}{bone}{to} make known the mystery of the gospel,}
[20] \textcolor[cmyk]{0.99998,1,0,0}{For which I am an \fcolorbox{bone}{lime}{ambassador} in bonds: that therein I may speak boldly, as I ought \fcolorbox{bone}{bone}{to} speak.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{But that ye also may know my affairs, \emph{and} how I do, Tychicus, a beloved brother and faithful minister in the Lord, shall make known \fcolorbox{bone}{bone}{to} you all things:}
[22] \textcolor[cmyk]{0.99998,1,0,0}{Whom I have sent unto you for the same purpose, that ye might know our affairs, and \emph{that} he might comfort your hearts.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{Peace \emph{be} \fcolorbox{bone}{bone}{to} the brethren, and love with faith, from God the Father and the Lord Jesus Christ.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{Grace \emph{be} with all them that love our Lord Jesus Christ in sincerity. Amen.}