\subsection{Outlines from Billheimer}

\subsubsection{Unity of Our Salvation}

\textbf{Introduction:} Why do you suppose Jesus chose the process of birth to connect to His salvation? Simply put, birth is a beginning of everything in an individual. For nine months the individual developed inside its mother, depending on her for the very nutrition through which it could grow. When the baby is born, that cord of dependence is separated and he or she is on his or her own, in at least one sense. Babies are helpless in the beginning, but they should grow and begin to learn and do more for themselves as they grow.  Jesus told Nicodemus that the spiritual birth in many ways was like the physical birth. As much as we know medically today, there are still mysteries in this wonderful event of procreation. There is water in the physical birth \index[scripture]{John!John 03:03}  (John 3:3), which is a picture of the word of God or the Holy Spirit; often both are compared to water in the Bible. The new birth is supposed to be as much of a transformation and more than the physical birth ever is. Because it is what it is--a mystery we accept by faith--the Lord has used terms we understand better to grasp what this event in our life really is and should mean.:\footnote{10 May 2016, Clarence Billheimer}
\index[speaker]{Clarence Billheimer!Ephesians 2 (Unity of Our Salvation)}
\index[series]{Ephesians (Clarence Billheimer)!Ephesians 2 (Unity of Our Salvation)}
\index[date]{2016/05/10!Ephesians 2 (Unity of Our Salvation) (Clarence Billheimer)}
\begin{compactenum}[I.]
    \item \textbf{Our ways were ways of death} we were dead in trespasses and sins. We understand the process of death; we experience it one time or another when we lose a friend or loved one. That person is separated from us then. The unsaved man is spiritually dead-- separated from God.
    \item \textbf{Our walk was the way of the devil} we walked according to the course of this world, under the influence of the devil. It does not necessarily mean we had to be in any certain form of sin (drunkenness, drug addiction, adultery, etc.), just that we were guided and influenced one way or another by the devil.
    \item \textbf{Our words were the words of depravity} the word “conversation” here primarily means manner of life, but speech is a vital part of that. Therefore, even if we tried to keep our speech clean from cursing and the like, it was still not properly spiritually centered and focused. Neither was our manner of life, even if we lived what the world calls a moral one.
    \item \textbf{Our will was the will of desire for self} we had “I” trouble, and in some sense we still struggle with that. But the unsaved man is not spiritually concerned about anyone else. Nor is he usually that socially concerned. His main man is himself. Whatever satisfies him is right and good; as the last verse in Judges puts it, “Every man did that which was right in his own eyes.”
    \item \textbf{Our wonderful transformation is a transformation of and by the Divine!} It is totally of God, as verses 8 and 9 say, yet it is with a desired goal to produce good works as verse 10 says. He made us alive from death. He delivered us from the way of the devil. He rescued us from the doom of our depravity. And His Holy Spirit is now there to help us have a desire for things of God and the souls of mankind.
\end{compactenum}
\textbf{Conclusion:} In God’s mind, of course, the work is already signed, sealed, and delivered. We are as much in heaven already in His mind as if we were really there. \index[scripture]{Romans!Romans 08:29, 30}  Romans 8:29,30 contains that assurance for us; the passage goes on then to modify that standing of ours with Him. With the new birth is to come new desires, less depravity, and ultimately eternal life. What a total transformation this has the potential to be and in God’s eyes already is! Yet, we still have the choice and ability to make it grow and prosper or be anemic. Certainly, in light of the great transformation miracle God performs totally by grace, it ought to be impetus for us to LIVE that transformed life as best as we can with His help.


