\chapter{Ephesians 5}\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{ONE BODY}}\\ (Ephesians 5:1-33) \begin{compactenum}[I.][8]
    \item \textbf{Unfeelingness} \index[scripture]{Ephesians!Ephesians 5:01} (Ephesians 5:1)
    \item \textbf{Fornication} \index[scripture]{Ephesians!Ephesians 5:03} (Ephesians 5:3)
    \item \textbf{Filthiness} \index[scripture]{Ephesians!Ephesians 5:04} (Ephesians 5:4)
    \item \textbf{Foolishness} \index[scripture]{Ephesians!Ephesians 5:04} (Ephesians 5:1)
    \item \textbf{Frivolity} \index[scripture]{Ephesians!Ephesians 5:06} (Ephesians 5:6)
    \item \textbf{Unfruitfulness} \index[scripture]{Ephesians!Ephesians 5:11} (Ephesians 5:11)
    \item \textbf{Fellowship with Darkness} \index[scripture]{Ephesians!Ephesians 5:01} (Ephesians 5:1)
\end{compactenum}}

% \textcolor[cmyk]{0.99998,1,0,0}{
% \footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/N/Eph/1}{\textcolor[cmyk]{0.99998,1,0,0}{Ephesians Audio}}}
\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/N/Eph/1}{\textcolor[cmyk]{0.99998,1,0,0}{Ephesians Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{Be ye therefore \fcolorbox{bone}{lime}{followers} of God, as dear children;}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And walk in love, as Christ also hath loved us, and hath given himself for us an offering and a sacrifice to God for a sweetsmelling savour.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{But \fcolorbox{bone}{lime}{fornication}, and all uncleanness, or covetousness, let it not be once named among you, as becometh saints;}
[4] \textcolor[cmyk]{0.99998,1,0,0}{Neither \fcolorbox{bone}{lime}{filthiness}, nor foolish talking, nor jesting, which are not convenient: but rather giving of thanks.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{For this ye know, that no whoremonger, nor unclean person, nor covetous man, who is an idolater, hath any inheritance in the kingdom of Christ and of God.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{Let no man deceive you with vain words: for because of these things cometh the wrath of God upon the children of disobedience.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{Be not ye therefore partakers with them.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{For ye were sometimes darkness, but now \emph{are} \emph{ye} light in the Lord: walk as children of light:}
[9] \textcolor[cmyk]{0.99998,1,0,0}{(For the fruit of the Spirit \emph{is} in all goodness and righteousness and truth;)}
[10] \textcolor[cmyk]{0.99998,1,0,0}{Proving what is acceptable unto the Lord.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And have no fellowship with the \fcolorbox{bone}{lime}{unfruitful} works of darkness, but rather reprove \emph{them}.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{For it is a shame even to speak of those things which are done of them in secret.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{But all things that are reproved are made manifest by the light: for whatsoever doth make manifest is light.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore he saith, Awake thou that sleepest, and arise from the dead, and Christ shall give thee light.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{See then that ye walk circumspectly, not as fools, but as wise,}
[16] \textcolor[cmyk]{0.99998,1,0,0}{Redeeming the time, because the days are evil.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Wherefore be ye not unwise, but understanding what the will of the Lord \emph{is}.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{And be not \fcolorbox{bone}{lime}{drunk with wine}, wherein is excess; but be filled with the Spirit;}
[19] \textcolor[cmyk]{0.99998,1,0,0}{Speaking to yourselves in psalms and hymns and spiritual songs, singing and making melody in your heart to the Lord;}
[20] \textcolor[cmyk]{0.99998,1,0,0}{Giving thanks always for all things unto God and the Father in the name of our Lord Jesus Christ;}
[21] \textcolor[cmyk]{0.99998,1,0,0}{Submitting yourselves one to another in the fear of God.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{Wives, submit yourselves unto your own husbands, as unto the Lord.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{For the husband is the head of the wife, even as Christ is the head of the church: and he is the saviour of the body.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{Therefore as the church is subject unto Christ, so \emph{let} the wives \emph{be} to their own husbands in every thing.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{Husbands, love your wives, even as Christ also loved the church, and gave himself for it;}
[26] \textcolor[cmyk]{0.99998,1,0,0}{That he might sanctify and cleanse it with the washing of water by the word,}
[27] \textcolor[cmyk]{0.99998,1,0,0}{That he might present it to himself a glorious church, not having spot, or wrinkle, or any such thing; but that it should be holy and without blemish.}
[28] \textcolor[cmyk]{0.99998,1,0,0}{So ought men to love their wives as their own bodies. He that loveth his wife loveth himself.}
[29] \textcolor[cmyk]{0.99998,1,0,0}{For no man ever yet hated his own flesh; but nourisheth and cherisheth it, even as the Lord the church:}
[30] \textcolor[cmyk]{0.99998,1,0,0}{For we are members of his body, of his flesh, and of his bones.}
[31] \textcolor[cmyk]{0.99998,1,0,0}{For this cause shall a man leave his father and mother, and shall be joined unto his wife, and they two shall be one flesh.}
[32] \textcolor[cmyk]{0.99998,1,0,0}{This is a great mystery: but I speak concerning Christ and the church.}
[33] \textcolor[cmyk]{0.99998,1,0,0}{Nevertheless let every one of you in particular so love his wife even as himself; and the wife \emph{see} that she reverence \emph{her} husband.}